---
title: "St. Jude OS data CNV analysis"
author: "Matt Cannon"
date: 06-03-2022
output:
    html_document:
        code_folding: hide
        toc: yes
        toc_depth: 3
        toc_float:
            collapsed: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    cache = TRUE,
    fig.height = 10,
    fig.width = 20,
    dpi = 300)
```

# St. Jude OS data CNV analysis

## Goals:

We want to characterize the CNV data from St. Jude OS samples in order to
determine if the CNVs are consistent across samples within a patient. This will
tell us if these tumors are genomically stable or if there are ongoing
rearrangements. We also want to determine if there are sub-clones within a
single patient which would be revealed by distinct CNV patterns within a patient.

## Samples:

For this analysis we got access to many St. Jude OS samples. We also included
our single-cell sequencing data which we treated as bulk for the purposes of
these analyses.

# Workflow

## Load libraries
```{r libraries, cache=FALSE, eval=TRUE}
library(tidyverse)
theme_set(theme_bw())
theme_update(plot.title = element_text(hjust = 0.5))
library(gt)
```

## Make up directory structure
```{bash mkdirs, eval=TRUE}
for directoryName in \
  misc \
  slurmOut \
  input\split \
  output \
  output/aligned \
  output/figures \
  output/counts \
  output/varscan/copynumber/ \
  output/vcfs \
  output/vcfs/realignSummary \
  output/vcfs/p53Char \
  output/vcfs/p53Char/clinVar
do
  if [ ! -d ${directoryName} ]
  then
    mkdir -p ${directoryName}
  fi 
done
```

## Prepare files that contain links to DNAnexus data
Had to do this by hand due to the links expiring after 24 hours

We had a lot of trouble downloading large bam files from DNAnexus. The downloads
frequently got interupted. To get around this, I split the files in DNAnexus
into smaller chunks to make interuptions less likely. I also wrote the code
below to automatically resume the downloads if the download was interupted. I
had the script check the md5sums to be sure that the file wasn't corrupted
during download. The original file is then re-generated using cat and md5sum
checked again.

Don't forget to dos2unix the .txt files before running!

```{bash prepDl, eval=FALSE}
perl ../scripts/prepDownloadFile.pl \
  --linkFile misc/DNAnexus_export_urls-20210926-103118.txt \
  --md5File misc/allMd5.txt \
    > misc/batch1DownloadFile.txt

perl ../scripts/prepDownloadFile.pl \
  --linkFile misc/DNAnexus_export_urls-20210927-085055.txt \
  --md5File misc/allMd5.txt \
    > misc/batch2DownloadFile.txt

perl ../scripts/prepDownloadFile.pl \
  --linkFile misc/DNAnexus_export_urls-20210928-082401.txt \
  --md5File misc/allMd5.txt \
    > misc/batch3DownloadFile.txt

perl ../scripts/prepDownloadFile.pl \
  --linkFile misc/DNAnexus_export_urls-20210929-083226.txt \
  --md5File misc/allMd5.txt \
    > misc/batch4DownloadFile.txt

perl ../scripts/prepDownloadFile.pl \
  --linkFile misc/DNAnexus_export_urls-20210930-084226.txt \
  --md5File misc/allMd5.txt \
    > misc/batch5DownloadFile.txt
    
perl ../scripts/prepDownloadFile.pl \
  --linkFile misc/DNAnexus_export_urls-20211001-084849.txt \
  --md5File misc/allMd5.txt \
    > misc/batch6DownloadFile.txt
```

## Download split files from DNA nexus
I had to run these one by one manually due to how the data are organized
```{bash download, eval=FALSE}
sbatch sbatchCmds/forceDownload_1.sh
sbatch sbatchCmds/forceDownload_2.sh
sbatch sbatchCmds/forceDownload_3.sh
sbatch sbatchCmds/forceDownload_4.sh
sbatch sbatchCmds/forceDownload_5.sh
sbatch sbatchCmds/forceDownload_6.sh
```

## Downloaded the md5 data for the raw bam files
```{bash getRawMd5s, eval=FALSE}
cat misc/rawMd5s/rawBamMd5_md5sum_job-G5FQ* > misc/rawBamMd5s.txt
```

## Recombine the split files and check md5sums
```{bash recombineSplit, eval=FALSE}
sbatch sbatchCmds/catSplitFiles.sh
```

## Make up symbolic links to previously analyzed data so we can analyze those as well
```{bash symLinks, eval=FALSE}
for original in S0113 S0114 S0115 S0116 S0126 S0127 S0128
do
    ln -s \
        /home/gdrobertslab/lab/Counts/${original}/possorted_bam.bam \
        input/${original}.bam
done

# Some of the samples were already in the input folder and don't need symLinks
for original in \
        SJOS046149_R1 SJOS046149_R2 SJOS046149_X1 SJOS031478_D1 \
        SJOS031478_D2 SJOS031478_D3
do
    ln -s \
        ~/analyses/roberts/stjude/rawData/${original}.WholeGenome.bam \
        input/${original}.WholeGenome.bam
done
```

## Make up a list of all chromosomes in the hg38 genome
Kicked out the unknown and random chromosomes
```{bash makeChrList, eval=TRUE}
cat /reference/homo_sapiens/hg38/ucsc_assembly/illumina_download/Sequence/WholeGenomeFasta/genome.fa.fai | \
  grep -v "chrUn\|random\|EBV" \
    > misc/chrList.txt
```

## Realign the bam files using a mixed human/mouse reference
```{bash realign, eval=FALSE}
if [ ! -d /gpfs0/scratch/mvc002/roberts/stjude/realigned ]
then
    mkdir -p /gpfs0/scratch/mvc002/roberts/stjude/realigned
fi

sbatch sbatchCmds/realign.sh
```

## Call CNVs using varscan
```{bash callCNVnumber, eval=FALSE}
sbatch sbatchCmds/mpileupVarscan.sh
```

## Refine CNV calls using varscan copycaller
```{bash callCNVcopycaller, eval=FALSE}
sbatch sbatchCmds/varScanCopycaller.sh
```

### Plot the distribution of CNVs found by copynumber
```{r plotCNVs, eval=TRUE}
pdf(file = "output/figures/CNVdistribution_copynumber.pdf")
for (sample_name in list.dirs(path = "output/varscan/copynumber",
                              full.names = FALSE,
                              recursive = FALSE)) {
    print(read_tsv(list.files(path = paste("output/varscan/copynumber/",
                                           sample_name,
                                           sep = ""),
                             pattern = "*.copynumber",
                             full.names = TRUE),
                   show_col_types = FALSE) %>%
        sample_n(1000000) %>%
        select(log2_ratio) %>%
        mutate(ratio = 2^log2_ratio) %>%
        ggplot(aes(x = ratio)) +
        geom_histogram(bins = 300) +
        geom_vline(xintercept = 1) +
        scale_x_log10() +
        geom_vline(xintercept = 2) +
        geom_vline(xintercept = 0.5) +
        ggtitle(sample_name))
}
dev.off()
```

## Calculate the distance between samples based on CNVs
This approach has the issue that normalization isn't perfect across the samples
due to the extensive number of genomic changes. This artificially increases the
distance between similar samples. This likely will not be used in the paper.
```{bash varscanMatrix, eval=FALSE}
perl scripts/varscanToMatrix.pl \
    -v \
    --fileList "output/varscan/copycaller/S*/*chr*.txt" \
        > output/varscan/varscan_distMatrix.txt

perl scripts/varscanToMatrix_threshhold.pl \
    -v \
    --fileList "output/varscan/copycaller/S011*/*chr*.txt" \
        > output/varscan/varscan_distMatrix_threshhold.txt
```

## Combine the varscan outputs into one file
```{bash varscanCombine, eval=FALSE}
sbatch sbatchCmds/combineVarscan.sh
```

## Make plots of the CNV calls across all the samples
```{r plotVarscan, eval=TRUE}
large_bin_size <- 100000

combined_data <- read_tsv("output/varscan/combined_calls.txt",
                          show_col_types = FALSE) %>%
    mutate(chr_num = str_remove(chr, "chr") %>%
                as.numeric()) %>%
    arrange(chr_num, bin) %>%
    mutate(order = seq_len(nrow(.)),
           larger_bin = floor(bin / large_bin_size) * large_bin_size) %>%
    pivot_longer(cols = c(-chr, -bin, -order, -chr_num, -larger_bin),
                 names_to = "sample",
                 values_to = "log_ratio")

patient_key <- data.frame(
    patient = unique(combined_data$sample) %>%
        str_remove("_.+") %>%
        str_replace("S0126", "SJOS030645") %>%
        str_replace("S0127", "SJOS030645") %>%
        str_replace("S0128", "SJOS030645") %>%
        str_replace("S0114", "SJOS031478") %>%
        str_replace("S0116", "SJOS031478") %>%
        str_replace("S0113", "SJOS046149") %>%
        str_replace("S0115", "SJOS046149"),
    sample_type = unique(combined_data$sample) %>%
        str_replace("^S0.+", "Xenograft") %>%
        str_replace(".+_X.+", "Xenograft") %>%
        str_replace(".+_D.+", "Diagnosis") %>%
        str_replace(".+_M.+", "Metastasis") %>%
        str_replace(".+_R.+", "Relapse"),
    sample = unique(combined_data$sample))

combined_data <- full_join(combined_data, patient_key)

chr_cols <- sample(rainbow(length(unique(combined_data$chr))),
                   length(unique(combined_data$chr)),
                   replace = FALSE)

for (patient_name in unique(patient_key$patient)) {
    plot_name <- combined_data %>%
        filter(patient == patient_name) %>%
        group_by(chr, sample, larger_bin) %>%
        summarize(log_ratio = median(log_ratio),
                order = min(order),
                .groups = "drop") %>%
        ggplot(aes(x = order,
                    y = log_ratio,
                    color = chr)) +
        geom_hline(yintercept = 0, color = "black") +
        geom_point(alpha = 0.5,
                    size = 0.5) +
        scale_color_manual(values = chr_cols) +
        labs(y = "Copy number log ratio",
             x = "") +
        facet_wrap(~ sample, ncol = 1)

    ggsave(paste0("output/figures/varscan",
                 patient_name,
                 ".png"),
           plot = plot_name,
           width = 20,
           height = 8)
}

## Take a look at regions commonly amplified/deleted across samples
unique_clones <- c("SJOS001101_M4",
                   "SJOS001111_M1",
                   "SJOS001116_X2",
                   "SJOS001121_X2",
                   "SJOS001126_X1",
                   "SJOS013768_X1",
                   "SJOS016016_X1",
                   "SJOS030101_R1",
                   "SJOS030645_D2",
                   "SJOS031478_D3",
                   "SJOS046149_R2",
                   "SJOS001105_R1")

combined_data %>%
    filter(sample %in% unique_clones) %>%
    group_by(chr, bin) %>%
    summarize(mean_ratio = median(log_ratio),
              order = min(order),
              .groups = "drop") %>%
    ggplot(aes(x = bin,
               y = mean_ratio,
               color = chr)) +
    geom_hline(yintercept = 0, color = "black") +
    geom_point(alpha = 0.5,
               size = 0.5) +
    labs(x = "",
         y = "Mean copy number ratio") +
    facet_wrap(~ chr, scales = "free_x") +
    theme(legend.position = "none")

ggsave("output/figures/clonal_mean_CNV.png",
       width = 15,
       height = 10)

high_chr3 <- combined_data %>%
    filter(sample %in% unique_clones) %>%
    group_by(chr, bin) %>%
    summarize(mean_ratio = median(log_ratio),
              order = min(order),
              .groups = "drop") %>%
    filter(chr == "chr3" & mean_ratio < -0.5)
```

## Look at correlation of CNVs between samples
```{r CNVcorr, eval=TRUE}
cnv_cor <- read_tsv("output/varscan/combined_calls.txt",
                     col_names = TRUE,
                     show_col_types = FALSE) %>%
    mutate(chr_bin = paste(chr, bin, sep = "_"), .keep = "unused") %>%
    column_to_rownames("chr_bin") %>%
    cor()

patient_key <- data.frame(patient = rownames(cnv_cor) %>%
                                str_remove("_.+") %>%
                                str_replace("S0126", "SJOS030645") %>%
                                str_replace("S0127", "SJOS030645") %>%
                                str_replace("S0128", "SJOS030645") %>%
                                str_replace("S0114", "SJOS031478") %>%
                                str_replace("S0116", "SJOS031478") %>%
                                str_replace("S0113", "SJOS046149") %>%
                                str_replace("S0115", "SJOS046149"),
                          sample_type = rownames(cnv_cor) %>%
                                str_replace("^S0.+", "Xenograft") %>%
                                str_replace(".+_X.+", "Xenograft") %>%
                                str_replace(".+_D.+", "Diagnosis") %>%
                                str_replace(".+_M.+", "Metastasis") %>%
                                str_replace(".+_R.+", "Relapse"),
                          sample_2 = rownames(cnv_cor)) %>%
    column_to_rownames("sample_2")

long_cor <-
    cnv_cor %>%
    as.data.frame() %>%
    rownames_to_column("sample_1") %>%
    pivot_longer(-sample_1,
                 names_to = "sample_2",
                 values_to = "cor") %>%
    left_join(patient_key %>%
                rownames_to_column("sample_1") %>%
                rename(patient_1 = patient) %>%
                select(-sample_type)) %>%
    left_join(patient_key %>%
                rownames_to_column("sample_2") %>%
                rename(patient_2 = patient) %>%
                select(-sample_type)) %>%
    mutate(within = patient_1 == patient_2,
           sample_1 = fct_reorder(sample_1, patient_1),
           sample_2 = fct_reorder(sample_2, patient_2)) %>%
    filter(sample_1 != sample_2) %>%
    arrange(patient_1)

## Try to id clones
clone_table <- tibble(sample_1 = character(),
                      clone_num = factor())
claimed_list <- character()
cor_cutoff <- 0.4
clone_num <- 1

for (sample_name in rownames(cnv_cor)) {
    if (!sample_name %in% claimed_list) {
        new_claimed <-
            long_cor %>%
            filter(sample_1 == sample_name &
                    cor >= cor_cutoff &
                    within == TRUE) %>%
            select(sample_2, cor) %>%
            mutate(clone_num = as.factor(clone_num)) %>%
            bind_rows(tibble(clone_num = as.factor(clone_num),
                             sample_2 = sample_name,
                             cor = 1))
        clone_table <-
            rbind(clone_table, new_claimed)
        claimed_list <- c(claimed_list, sample_name, new_claimed$sample_2)
        clone_num <- clone_num + 1
    }
}


clone_table <-
    clone_table %>%
    group_by(sample_2) %>%
    arrange(cor * -1, .by_group = TRUE) %>%
    slice_head(n = 1) %>%
    ungroup() %>%
    select(-cor)

long_cor <- full_join(long_cor, clone_table, by = "sample_2")

# Mean within patient correlation
long_cor %>%
    filter(within == TRUE) %>%
    pull(cor) %>%
    summary()

# # Mean correlation within a clone
# long_cor %>%
#     select(sample_2, patient_2, cor, clone_num) %>%
#     group_by(patient_2, clone_num) %>%
#     summarize(cor = mean(cor)) %>%
#     pull(cor) %>%
#     summary()

# Get number of patients with >1 clone
long_cor %>%
    select(patient_2, clone_num) %>%
    arrange(patient_2) %>%
    distinct() %>%
    pull(patient_2) %>%
    table()

# Mean within clone correlation
long_cor %>%
    full_join(clone_table %>%
                rename(sample_1 = sample_2,
                       clone_2 = clone_num)) %>%
    filter(clone_num == clone_2) %>%
    pull(cor) %>%
    summary()

# Mean correlatin within a patient between divergent clones
long_cor %>%
    full_join(clone_table %>%
                rename(sample_1 = sample_2,
                       clone_2 = clone_num)) %>%
    filter(patient_1 == patient_2 &
           clone_num != clone_2) %>%
    pull(cor) %>%
    summary()

# Mean correlation between patients
long_cor %>%
    full_join(clone_table %>%
                rename(sample_1 = sample_2,
                       clone_2 = clone_num)) %>%
    filter(patient_1 != patient_2) %>%
    pull(cor) %>%
    summary()

# Correlation between xenografts and original samples within a single clone and patient
long_cor %>%
    full_join(clone_table %>%
                rename(sample_1 = sample_2,
                       clone_2 = clone_num)) %>%
    left_join(patient_key %>%
                rownames_to_column("sample_1") %>%
                rename(type_1 = sample_type) %>%
                select(-patient)) %>%
    left_join(patient_key %>%
                rownames_to_column("sample_2") %>%
                rename(type_2 = sample_type) %>%
                select(-patient)) %>%
    filter(patient_1 == patient_2 &
           clone_num == clone_2 &
           type_1 == "Xenograft" &
           type_2 != "Xenograft") %>%
    select(-within, -patient_1, -patient_2) %>%
    pull(cor) %>%
    summary()

ggplot(long_cor, aes(x = cor)) +
    geom_histogram(bins = 200) +
    facet_wrap(~ within, ncol = 1)

# correlation of about 0.4 seems to be the upper bound of non-related samples

n_clones <- max(as.numeric(long_cor$clone_num))

text_col <-
    long_cor %>%
    full_join(tibble(clone_num = seq_len(n_clones) %>%
                        as.factor(),
                    text_col = rainbow(n = n_clones) %>%
                        sample(size = n_clones))) %>%
    mutate(group = paste(patient_2, sample_2)) %>%
    select(group, text_col) %>%
    distinct() %>%
    arrange(group) %>%
    pull(text_col)

ggplot(long_cor, aes(x = paste(patient_1, sample_1),
                     y = paste(patient_2, sample_2),
                     fill = cor)) +
    geom_tile() +
    scale_fill_gradient2(low = "blue",
                         mid = "white",
                         high = "red",
                         midpoint = 0.5) +
    theme(axis.text.y = element_text(colour = text_col))


patient_key <- patient_key %>%
    rownames_to_column("sample_2") %>%
    full_join(clone_table) %>%
    column_to_rownames("sample_2") %>%
    rename(clone = clone_num,
           `sample type` = sample_type) %>%
    relocate(`sample type`, .after = last_col())# %>%
#    select(-`sample type`)

col_patient <- list(patient = c("#a6cee3",
                                "#1f78b4",
                                "#b2df8a",
                                "#33a02c",
                                "#fb9a99",
                                "#e31a1c",
                                "#fdbf6f",
                                "#ff7f00",
                                "#cab2d6",
                                "#6a3d9a",
                                "#ffff99",
                                "#b15928"),
                    clone = c("#96FF00",
                              "#00FFD2",
                              "#FF00B4",
                              "#2b754e",
                              "#3CFF00",
                              "#FF5A00",
                              "#F000FF",
                              "#9600FF",
                              "#3C00FF",
                              "#F0FF00",
                              "#FFB400",
                              "#0078FF",
                              "#001EFF",
                              "#00FF1E",
                              "#FF0000",
                              "#00D2FF",
                              "#FF005A"),
                    `sample type` = c("#a6cee3",
                                    "#1f78b4",
                                    "#b2df8a",
                                    "#33a02c"))

names(col_patient$patient) <- patient_key$patient %>%
    as.factor() %>%
    levels()

names(col_patient$`sample type`) <- patient_key$`sample type` %>%
    as_factor() %>%
    levels()

names(col_patient$clone) <- levels(clone_table$clone_num)

png("output/figures/cnv_correlation_heatmap.png",
    width = 3500,
    height = 3000,
    res = 300)
pheatmap::pheatmap(cnv_cor,
                   annotation_row = patient_key,
                   annotation_col = patient_key,
                   annotation_colors = col_patient)
dev.off()

```

# SNP calling

## Call snps using bcftools mpileup and filter SNPs
Filter out indels and SNPs with qual < 20 and depth < 20
```{bash snpCalling, eval=FALSE}
# Make up a list of chromosomes to analyze for use by parallel
grep "^>" \
    /reference/homo_sapiens/hg38/ucsc_assembly/illumina_download/Sequence/WholeGenomeFasta/genome.fa \
    | grep -v "random\|chrUn\|chrEBV" \
    | perl -pe 's/>//' \
        > misc/chrList.txt

sbatch sbatchCmds/callVariants.sh
```

```{bash indexSnpCalling, eval=FALSE}
sbatch sbatchCmds/indexVcfs.sh
```

## Calculate distance between samples based on SNP calls
```{bash snpDist, eval=FALSE}
module load GCC/9.3.0 \
            GCCcore/9.3.0 \
            BCFtools/1.11 \
            SAMtools/1.15

perl scripts/vcfToMatrix_parallel.pl \
    --fileList "output/vcfs/S*vcf.gz" \
    --threads 20 \
        > output/vcfs/snpDistanceMatrix.txt
```

## Check P53 for mutations using SnpEff
```{bash p53, eval=FALSE}
sbatch sbatchCmds/TP53MutChar.sh

wget https://ftp.ncbi.nlm.nih.gov/pub/clinvar/vcf_GRCh38/clinvar_20220416.vcf.gz
mv clinvar_20220416.vcf.gz misc/
zcat misc/clinvar_20220416.vcf.gz \
    | awk '$1 ~ /^#/ || \
           $1 == 17 && \
           $2 >= 7600000 && \
           $2 <= 7690000 \
           {print}' \
    | perl -pe 's/^17/chr17/' \
    | gzip \
    > misc/clinvar_TP53.vcf.gz
```

## Merge clinvar data with TP53Muts.txt
```{bash clinvarCombine, eval=FALSE}
combineClinvar.sh
```

```{r germlineP53, eval=TRUE}
filter_list <- function(x) {
    str_split(x, ",") %>%
    unlist() %>%
    str_subset("TP53") %>%
    str_c(collapse = ",")
}

file_list <- list.files("output/vcfs/p53Char/clinVar",
                        pattern = ".+_G.+",
                        full.names = TRUE)

combined_data <- tibble(sample = character())

for (file_name in file_list) {
    combined_data <-
        read_tsv(file_name,
                 col_names = TRUE,
                 col_types = cols(.default = "c")) %>%
        filter(grepl("TP53", ANN)) %>%
        rowwise() %>%
        mutate(ANN = filter_list(ANN),
               sample = str_match(file_name, ".+/(.+).txt")[2]) %>%
        filter(ANN != "") %>%
        bind_rows(combined_data) %>%
        relocate(sample, CLNSIG, ANN)
}

write_tsv(combined_data,
          file = "output/vcfs/p53Char/p53Char_combined_germline.txt")
```

```{bash p53Combine, eval=TRUE}
perl scripts/cmpVarscanCalls.pl \
    --binSize 100 \
    --inputFiles "output/varscan/copycaller/*/*chr17.txt" \
        > output/varscan/combined_calls_chr17.txt
```

## Plot P53 CNV data
```{r p53Cnv, eval=TRUE}
P53_loc <- list(min = 7661779,
                max = 7687538)

combined_data <- read_tsv("output/varscan/combined_calls_chr17.txt",
                          show_col_types = FALSE) %>%
    mutate(chr_num = str_remove(chr, "chr") %>%
                as.numeric()) %>%
    filter(chr_num == 17 & bin >= 7550000 & bin <= 7800000) %>%
    arrange(chr_num, bin) %>%
    pivot_longer(cols = c(-chr, -bin, -chr_num),
                 names_to = "sample",
                 values_to = "log_ratio")

patient_key <- data.frame(
    patient = unique(combined_data$sample) %>%
        str_remove("_.+") %>%
        str_replace("S0126", "SJOS030645") %>%
        str_replace("S0127", "SJOS030645") %>%
        str_replace("S0128", "SJOS030645") %>%
        str_replace("S0114", "SJOS031478") %>%
        str_replace("S0116", "SJOS031478") %>%
        str_replace("S0113", "SJOS046149") %>%
        str_replace("S0115", "SJOS046149"),
    sample_type = unique(combined_data$sample) %>%
        str_replace("^S0.+", "Xenograft") %>%
        str_replace(".+_X.+", "Xenograft") %>%
        str_replace(".+_D.+", "Diagnosis") %>%
        str_replace(".+_M.+", "Metastasis") %>%
        str_replace(".+_R.+", "Relapse"),
    sample = unique(combined_data$sample))

combined_data <- full_join(combined_data, patient_key) %>%
    mutate(amplification = if_else(log_ratio > 0.5,
                                   "amplification",
                                   if_else(log_ratio < -0.5,
                                           "deletion",
                                           "normal")))

ggplot(combined_data,
       aes(x = bin,
           y  = sample,
           fill = log_ratio)) +
    geom_tile() +
    scale_fill_gradient2(low = "#8e0152",
                         mid = "white",
                         high = "#276419") +
    facet_grid(patient ~ .,
               scales = "free_y",
               space = "free") +
    theme(strip.text.y.right = element_text(angle = 0)) +
    geom_vline(xintercept = P53_loc$min,
               linetype = "dashed",
               colour = "red") +
    geom_vline(xintercept = P53_loc$max,
               linetype = "dashed",
               colour = "red") +
    labs(x = "Chromosome 17 position",
         y = "",
         title = "TP53 copy numbers")

ggsave(file = "output/figures/p53Cnv_chr17.png",
       width = 10,
       height = 10)
```

```{r sessionInfo, eval=TRUE, cache=FALSE}
sessionInfo()
```